APIs for hyperparameter optimization in scikit-learn

### 2013-05-13 paper.tex
elaborate on the H -> X -> Y notation

\section{The hyperparameter optimization problem}

@@

Construction and application of an estimator object
proceeds in a way that is somewhat reminiscent of partial function application.
The constructor, \texttt{\_\_init\_\_}\footnote{
  Strictly speaking, \texttt{\_\_init\_\_} is Python's
  class \textit{initialization} method,
  while \texttt{\_\_new\_\_} is the constructor.
  The distinction is not relevant to the present description of scikit-learn.}
takes a set of named (hyper-)parameters
and attaches these to the estimator as public attributes.\footnote{
  The Python language does not actually distinguish between public and private
  attributes and methods,
  but by convention, any identifier prefixed with an underscore (\texttt{\_})
  is considered ``a non-public part of the API\ldots
  an implementation detail and subject to change without notice.''
  \Citep{pythontut}
  }
It never performs actual learning, nor does it even see a training set.

>>>>

\section{The hyperparameter optimization problem}
\label{hyperparams}

@@

Construction and application of an estimator object
proceeds in a way that is similar to partial function application,
mirroring the $L : \mathcal{H} \to \mathcal{X} \to \mathcal{Y}$ notation
given for the supervised learning problem in Section~\ref{hyperparams}.
The constructor, \texttt{\_\_init\_\_}\footnote{
  Strictly speaking, \texttt{\_\_init\_\_} is Python's
  class \textit{initialization} method,
  while \texttt{\_\_new\_\_} is the constructor.
  The distinction is not relevant to the present description of scikit-learn.}
takes a set of named (hyper-)parameters
and attaches these to the estimator as public attributes.\footnote{
  The Python language does not actually distinguish between public and private
  attributes and methods,
  but by convention, any identifier prefixed with an underscore (\texttt{\_})
  is considered ``a non-public part of the API\ldots
  an implementation detail and subject to change without notice.''
  \Citep{pythontut}
  }
It never performs actual learning, nor does it even see a training set.
